Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-22 awipev-CO2.Rmd
edited and corrected chunk "Combine discrete and continous data"

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  )
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE))
#restore datetime, date which are mangled by the mutates above
d_all$datetime <- d_hour$datetime
d_all$date <- d_hour$date
d_all$month <- month(d_all$datetime)
```

@@

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  dplyr::group_by(date) %>%
  dplyr::summarize(
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE),
    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
    temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
  )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='date')
discrete <- left_join(discrete, pH_durafet_mean, by='date')

@@

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# ct
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ct, qflag_ct) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, phcalc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m

discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# Duplicate datetime in closest_datetime to do the left_join
d_all$closest_datetime <- d_all$datetime
discrete <- left_join(discrete, d_all%>%dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
```

>>>>

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                       date = d_hour$date,
                       month = month(d_hour$datetime))
```

@@

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  dplyr::group_by(date) %>%
  dplyr::summarize(
    datetime = mean(datetime, na.rm = TRUE),
      sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE),
    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
    temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
  )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='date')
discrete <- left_join(discrete, pH_durafet_mean, by='date')

@@

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# ct
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ct) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated ferrybox
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, phcalc_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated in situ
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, phcalc_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spec data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m

# durafet pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# calculated pCO2 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, pco2_calc_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# Duplicate datetime in closest_datetime to do the left_join
d_all$closest_datetime <- d_all$datetime
discrete <- left_join(discrete, d_all %>% dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
```
